Trade Reviews

### 2019-04-08 tradeReview.Rmd
Removed todo, check for league key environment variable

#### Fantasy team rosters
```{r}
source("R/yahoo_api.R")
league_string <- paste0("388.l.",Sys.getenv("LEAGUE_KEY"))
get_team_rosters(league_string) -> rosters

>>>>

#### Fantasy team rosters
```{r}
source("R/yahoo_api.R")
league_key <- Sys.getenv("LEAGUE_KEY")

if (identical("", league_key)) {
  stop("LEAGUE_KEY isn't set as R Environment variable")
} else {
  league_string <- paste0("388.l.",Sys.getenv("LEAGUE_KEY"))
  get_team_rosters(league_string) -> rosters  
}
```
